D3064R0: OOTA Execution on Real Implementations is Provably Vacuous

### 2023-12-17 ootavacuous.tex
Add Michael Wong's summary of debates on causality
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

>>>>

\section{Debates on Causality}
\label{sec:Debates on Causality}

This Appendix is provided as a service to readers who want to know more
about the ongoing debates on causality.
References may be found here:

{ \scriptsize
\url{https://docs.google.com/document/d/1MJ6pQ4TcWchUQvoI-qhLjdhPVYF14AytbTW3gr4-xag/edit?usp=sharing}
}

The concept of causality, the idea that events are caused by preceding
events in a predictable and consistent manner, is fundamental to many
scientific theories and our understanding of the world.
However, when it comes to the universe as a whole, particularly at the
most fundamental levels such as in quantum physics or the origins of
the universe, the idea of strict causality can become more complex.

In classical physics, causality is often described in terms of
deterministic laws, where events are determined by prior causes.
But at the quantum level, the behavior of particles can be probabilistic
and uncertain.
Quantum mechanics introduces a level of randomness and uncertainty that
challenges our classical notions of causality.

Additionally, when considering the origin of the universe (the Big Bang),
the laws of physics as we understand them break down at extremely high
densities and temperatures.
The conditions at the very beginning of the universe might not conform
to our classical understanding of causality, and some theories suggest
that time itself might have begun with the Big Bang, making it difficult
to define causality in a traditional sense within such a framework.

On the one hand, there is a strong case to be made that the universe
is causal.
Our understanding of physics is based on the principle of causality,
which states that every event has a cause.
This principle has been incredibly successful in explaining and predicting
the behavior of the universe at large scales.
Additionally, our own personal experience seems to confirm causality.
We constantly observe events being caused by other events, and we have
no reason to believe that this is an illusion.

However, there are also some challenges to the idea of a perfectly
causal universe.
One challenge comes from quantum mechanics, which suggests that some
events may be fundamentally non-causal.
For example, the collapse of a wave function in quantum mechanics seems
to be a random event, with no underlying cause.
Additionally, our understanding of the universe's origins is still
very limited.
We don't know whether the Big Bang itself had a cause, or whether it
was simply the beginning of everything.

In summary, while causality is a fundamental concept in our understanding
of the universe, its application and implications can become more complex,
especially at the quantum level and regarding the origin of the universe.
There are ongoing debates and explorations within physics and philosophy
about the nature of causality in these contexts.
